Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-11 2016-Weak-FH-Bisim/WeakBisim.tex
notation lemma7

\[Q\models{\openrule
	{
		\set{\beta^2},
		 \Pred^2,  
		\Post^2}
	{\ostate{s^2_{0}}\OTarrow {\alpha_Q}
		\ostate{s^2_{1}}}
}
\]

such that 
$s_i^{i\in L_Q}=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}={s'}_i^{i\in L_Q}$\\

$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta^1_h}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta^3_h}}}
\\
\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=h-1}^{0}\subst{\Post_j^1}\big)\land \Pred^2\bigotimes_{h=k}^{0}\subst{\Post_h^1}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=h-1}^{0}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=k}^{0}\subst{\Post_h^1}\big)
\\
\Post_Q=\bigotimes_{h=k'}^{0}\Post^3_h\subst{\Post^2}\bigotimes_{j=k}^{0}\subst{\Post^1_j}
$

@@

\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can necessarily make a tau open transition if the hole indexed $j_0$ makes a tau action. So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta^1_h},{\Pred^1_h},{\Post^1_h}   }
         {\ostate{s^1_h\uplus s^{i\in L}_{i} } \OTarrow {\tau} \ostate{s^1_{h+1}\uplus s^{i\in L}_{i}}}\]

\item For the observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
			\Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 },  
			\Post\uplus \Post^2}
{\ostate{s^{i\in L}_{i}\uplus s_0^2} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_1^2}}
	}
	\]

@@

By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $(2)$ and $(3)$ we obtain: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma'}, \Pred_c,
\Post_c}
         {\ostate{s^1_0\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{k'+1}^3}}}\] 
where
\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta^1_h}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta^3_h}}\]
\[
\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=h-1}^{0}\Post_i^1}\land
\left(Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_i^1}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=h-1}^{0}{\Post_i^3}\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}}
\end{array}
\]

\[\Post_c=(\bigotimes_{i=k'}^{0}{\Post_i^3})\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}
\]
Note that we have $s_i^{i\in L_Q}=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}={s'}_i^{i\in L_Q}$\\

Note also that $\Post$ only acts on variables of $P$ while $\Post^1_i$ only acts on state variables of $Q$. A
\end{proof}

@@

\begin{proof} Suppose we have:
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$\forall p\!\in\![0..m_1].P\models\openrule
    {\set{\beta^1_p},\Pred^1_p,\Post^1_p   }
         {\ostate{{(s^1_{pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s^1_{(p+1)i})}^{i\in L}}} \wedge
P\models\openrule
         {\set{\beta^2},\Pred^2,\Post^2 }
         {\ostate{({s_{0i}^2})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{1i}^2})^{i\in L}}}
\wedge\\
\forall p \in [0..m_2].P\models\openrule
         {
           \set{\beta^3_p},\Pred^3_p, \Post^3_p}
         { \ostate{(s^3_{pi})^{i\in L}} \OTarrow {\tau} \ostate{(s^3_{(p+1)i})^{i\in L}}}$ 
\\
where for all $i\in L$:\\
$s_i=s^1_{0 i} \wedge s^1_{(m_1+1) i}=s^2_{0i} \wedge  s^2_{1i}= s^3_{0 i} \wedge s^3_{(m_2+1) i}=s'_i$\\

$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}\\
\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred^1_p\bigotimes_{j=p-1}^{0}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_p^1}\land \bigwedge_{p=0}^{m_2}\!\Pred_p^3\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post^3_j}\subst{\Post^2}\!\! \bigotimes_{p=m_1}^{0}\subst{\Post_p^1}\big)\\
\Post=\bigotimes_{p=m_2}^{0}\Post^3_p\subst{\Post^2}\bigotimes_{j=m_1}^{0}\subst{\Post^1_j}
$\\

>>>>

\[\forall h\!\in\![0..k].Q\models\openrule
    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}
\]

\[Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha_Q}
		\ostate{s_{21}}}
}
\]

\[
\forall h \in [0..k'].Q\models\openrule
         {
           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}} \]

such that 
$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta_{1h}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}}}}
\\
\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\bigotimes_{j=h-1}^{0}\subst{\Post_j^1}\big)\land \Pred_2\bigotimes_{h=k}^{0}\subst{\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\big(\bigotimes_{j=h-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{h=k}^{0}\subst{\Post_{1h}}\big)
\\
\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\subst{\Post_2}\bigotimes_{j=k}^{0}\subst{\Post_{1j}}
$

@@

\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can necessarily make a tau open transition if the hole indexed $j_0$ makes a tau action. So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta_{1h}},{\Pred_{1h}},{\Post_{1h}}   }
         {\ostate{s_{1h}\uplus s^{i\in L}_{i} } \OTarrow {\tau} \ostate{s_{1(h+1)}\uplus s^{i\in L}_{i}}}\]

\item For the observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
			\Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 },  
			\Post\uplus \Post_2}
{\ostate{s^{i\in L}_{i}\uplus s_{20}} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_{21}}}
	}
	\]

@@

By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $(2)$ and $(3)$ we obtain: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma'}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where
\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}\]
\[
\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i^1}\land
\left(Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
\]

\[\Post_c=(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
\]
Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$. A
\end{proof}

@@

\begin{proof} Suppose we have:
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$\forall p\!\in\![0..m_1].P\models\openrule
    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}} \wedge
P\models\openrule
         {\set{\beta_2},\Pred_2,\Post_2 }
         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{21i}})^{i\in L}}}
\wedge\\
\forall p \in [0..m_2].P\models\openrule
         {
           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}}
         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$ 
\\
where for all $i\in L$:\\
$s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\

$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta_{1p}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta_{3p}}}}\\
\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\bigotimes_{j=p-1}^{0}\subst{\Post_{1j}}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}\!\! \bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\big)\\
\Post=\bigotimes_{p=m_2}^{0}\Post_{3p}\subst{\Post_2}\bigotimes_{j=m_1}^{0}\subst{\Post_{1j}}
$\\
